\problemname{Rocky Mountain}

The Rocky Mountain Cable (RMC) company is planning to run cables from
the top peak of the Rocky Mountains to lower points in the mountain
range, so that cable cars can be used to transport tourists to the
highest peak.  A cable must connect from one of the potential sites
to the highest peak in a straight line, but the cable cannot cross any
part of the mountain range.  However, the cable may coincide with a
slope.

In order to serve the most number of tourists, it is desirable to
connect the cable from the highest peak to the lowest possible
site.  Help the company determine the best possible site on the
left and the right of the highest peak.  If there are ties, choose the
leftmost site on the left, and the rightmost site on the right.

The mountain range is specified by $N$ sites $(x_i, y_i)$. One of 
these sites is the unique highest peak $(x_p, y_p)$ such that $1 < p < 
N$ and $y_p > y_i$ for all $i \neq p$.  Note that the highest peak
cannot be the first or the last site.  The entire mountain range is 
described by straight line segments connecting $(x_i, y_i)$ to 
$(x_{i+1}, y_{i+1})$ for $1 \leq i < N$, such that $x_i < 
x_{i+1}$.

\section*{Input} 
The first line of input contains the integer $N$
($3 \leq N \leq 5 \cdot 10^5$) which is the number of sites.  The
next $N$ lines each contains two integers $x_i$ and $y_i$, specifying
the $N$ sites.  The coordinates satisfy $0 \leq x_i, y_i \leq 10^9$.
It is guaranteed that there is a unique highest peak, and that
$x_i < x_{i+1}$ for all $1 \leq i < N$.

\section*{Output} 

On the first line, output the coordinates of the best site to the left
of the highest peak.  On the second line, output the coordinates of
the best site to the right of the highest peak.
