\problemname{Enchanted Maze}

Mila and her twin brother Liam have been trapped by an evil witch.  The
witch put the twins at different locations in a maze, and they must
find their way out of the maze before she releases her pet dragon.
The twins have asked you to help them escape the maze in the least
amount of time.

To make things even more difficult, the witch has placed a curse on
the twins.  Although the twins can attempt to move in any of the four
compass directions (North, South, East, West), they must attempt to
move in the same direction at the same time.  For example, if Mila
attempts to walk North for a step, Liam must also attempt to walk
North at the same time.  Each attempted move by the twins takes one
second to complete, regardless of whether the move was successful or
not.

The maze is represented by a rectangular grid, where each location can be one
of the following types:
\begin{itemize}
\item Start (\verb|S|): the starting positions of the
  twins.  There are exactly two starting locations, one for each twin.
\item Exit (\verb|E|): the twins escape if they are both at exit locations
  at the same time.  There are exactly two exit locations.
\item Open (\verb|.|): the twins may freely move in and out of
  this location.
\item Fixed Obstacle (\verb|#|): the twins may not move into this location.
\item Bottomless pit (\verb|*|): a twin moving into a pit is lost forever.
\item Raised obstacle (\verb|A, B, C, D|): these obstacles can be
  lowered by stepping on the corresponding switch.
\item Lowered obstacle (\verb|a, b, c, d|): these locations are considered
  open, but they can be raised by stepping on the corresponding switch.
\item Switch (\verb|1, 2, 3, 4|): switches that control the obstacles.
  Switch 1 controls obstacles labelled \verb|A| and \verb|a|, switch 2
  controls obstacles labelled \verb|B| and \verb|b|, switch 3 controls
  obstacles labelled \verb|C| and \verb|c|, and switch 4 controls
  obstacles labelled \verb|D| and \verb|d|.  There is at most one
  switch of each label, but each switch may control more than one
  obstacle.
\end{itemize}
The twins may not be in the same location at the same time.  If a twin
attempts to move into a fixed or raised obstacle, the twin will instead
remain stationary.  A twin that moves outside of the boundary of the
maze is lost forever.  They are also allowed to enter and leave the
starting and exit locations throughout their journey.

A switch is triggered when a twin moves onto a switch.  When a switch
is triggered, the corresponding obstacles are raised (if currently
lowered) or lowered (if currently raised).  The switch is not triggered if a twin is already on the
switch and remains stationary after an attempted move.

If a twin attempts to move into a raised obstacle at the same time the
other twin steps on the corresponding switch, the obstacle is still
considered raised and is only lowered at the end of the move.  A twin
may not move onto a switch if the other twin is moving onto or
remaining stationary at a corresponding lowered obstacle at the same
time.

\section*{Input} 
The first line of input contains two integers,
$2 \leq R \leq 10$ and $2 \leq C \leq 10$, specifying the number
of rows and columns in the maze.
The next R lines each contains C characters.  All possible characters
are specified above.  It is always possible for the twins to escape
the maze.


\section*{Output} 

Output the least number of seconds required for the twins to escape. 
